# Reproducible Research: Peer Assessment 1

## Loading and preprocessing the data
* Load necessary libraries:
```{r load_libraries, echo = TRUE}
  library(ggplot2)
```

* Assign function which loads data from csv file within zip archive:
```{r load_data, echo = TRUE}
load_data <- function() {
    file = "activity.zip"
    data <- read.csv2(unz(file, "activity.csv"), sep=",", header=TRUE)
    data$date <- as.Date(data$date, format="%Y-%m-%d")
    data$interval <- factor(data$interval)
    data
}
data <- load_data()
```

* Explore data summary:
```{r summary, echo = TRUE}
summary(data)
str(data)
```

## What is mean total number of steps taken per day?
* Histogram of the total number of steps taken each day:
```{r echo = FALSE, results = 'hide'}
# Set locale to english to avoid warnings "## Warning: font width unknown for character"
Sys.setlocale("LC_TIME", "English")
```
```{r make_histogram, echo = TRUE, fig.width = 10}
steps_per_day <- aggregate(steps ~ date, data = data, FUN = sum)
colnames(steps_per_day) <- c("date", "steps")
qplot(x = date, y = steps, geom = "histogram", fill = steps, stat = "identity", main = "The total number of steps taken each day", xlab = "Date", ylab = "Steps", data = steps_per_day)
```

* The mean and median total number of steps taken per day:
```{r echo = TRUE, results = 'hide'}
steps_mean <- mean(steps_per_day$steps)
steps_median <- median(steps_per_day$steps)
```

**Mean** - `r steps_mean`
  
**Median** - `r steps_median`

## What is the average daily activity pattern?
* Time series plot of the 5-minute interval and the average number of steps taken, averaged across all days:
```{r echo = TRUE}

```

* Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
